%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Entrepreneur in Residence \& AI Builder} % Job title
    {AI2 Incubator} % Organization
    {Seattle, WA} % Location
    {December 2020 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed the data architecture for the Callout.ai video chat Node.js application, with a RESTful API allowing users to save and update meeting artifacts tied to specific moments in the meeting.}
        \item {Built a robust front end application in React which allowed timeline aware annotation of meetings during video calls, as well as after them (full CRUD).}
        \item {Integrated with Google Docs API to create meeting summaries using NLP topic modeling.}
        \item {Implemented several API microservices in Node.js. to handle tasks like transcription and live chat over Websockets during meetings.}
        \item {Utilized Pulumi to write infrastructure as code and deploy our services to AWS EC2 clusters for development, testing, and production.}
        \item {Developed a computer vision AI model to detect laughter in real time during video calls.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sr. Software Engineer} % Job title
    {Moz Inc.} % Organization
    {Seattle, WA} % Location
    {May 2018 - December 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a service in Golang for triaging 3rd party customer data errors--utilized the JIRA API to create and update tickets automatically as issues were solved by the customer success team. This automated system replaced an entire team of 5 human workers.}
        \item {Built a zip code specific local search optimization tool on top of Postgres with GIS plugins. Built out APIs for this tool in Node.js. Worked on the frontend in React. Utilized Terraform to deploy the entire application to AWS EC2 clusters.}
        \item {Was responsible for the local search organization as a core member. Included on-call rotation work and delivering new features to customers via Node.js/React applications owned by the team.}
        \item {Participated in a company wide initiative to rewrite all microservices in Terraform and deploy them to AWS EC2 containers. Required rewriting and containerizing Ruby, JavaScript, CoffeeScript, Elixir, and Python services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Security Expert, UX Lead} % Job title
    {RumbleMonkey} % Organization
    {Seattle, WA} % Location
    {January 2017 - May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Transformed an existing desktop prototype written in Qt into a modern Electron application with an auditable, secure log of events that could be verified by the server in real time as interactions between two separate clients occured.}
        \item {Built a Golang service \& API facilitating a real time betting system for the trading card game Hearthstone.}
        \item {Developed a blockchain implementation which tracked user actions and tokens in the system, allowing secure real-money transactions between users.}
        \item {Interacted directly with customers to discover pain points in the software and solve them quickly and efficiently.}
        \item {Created a FFA multiplayer game in Unity3D, working directly with a game designer. Required hand coding all player interactions, game rules, and effects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering \& Consultant} % Job title
    {Rooster Park / Godaddy} % Organization
    {Kirkland, WA} % Location
    {February 2015 - December 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built Ember.js applications that replaced legacy account management UIs with mobile first SPAs.}
        \item {Designed and built Node.js proxy APIs that transformed legacy DB data from mySQL and made it available for consumption by product teams.}
        \item {Contributed to and maintained an internal library of React components which were used across the company to implement user facing UIs.}
        \item {Mentored junior developers and interns; acted as a code review gatekeeper \& SCRUM master.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Short Term Contractor} % Job title
    {Smashing Boxes} % Organization
    {Durham, NC / Remote} % Location
    {July 2014 - January 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented Ruby APIs exposing ImageMagick functionality and job processing to front end applications.}
        \item {Wrote AngularJS frontend applications for the firm's top clients.}
        \item {Integrated with 3rd party payment gateways using JavaScript SDKs.}
        \item {Built internal tooling for server orchestration and deployment in Ruby.}
        \item {Consolidated Chef cookbooks and developed a CLI for deploying new services and running cookbooks on multiple servers at once.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Engineer \& Consultant} % Job title
    {PugetWorks / Blue Nile} % Organization
    {Seattle, WA} % Location
    {April 2013 - June 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote ClojureScript in-browser text editor leveraging the Google Closure Compiler for a startup client.}
        \item {Worked at Blue Nile as a Java \& JavaScript consultant in an effort to rewrite the infinite scroll UI \& product search endpoints.}
        \item {Implemented a handlebars-like templating language in Java so that non-technical staff could update content on the Blue Nile website.}
        \item {Worked on a PostgreSQL / PostGIS \& Python service to store and quickly look up millions of data points over multiple shards for a startup client.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Ruby/Rails Engineer} % Job title
    {Intercon Logistics Management} % Organization
    {Seattle, WA} % Location
    {January 2012 - April 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built out Ruby APIs for all endpoints needed in the application.}
        \item {Wrote and maintained drivers for a magnetic card reader in C++.}
        \item {Worked closely with PugetWorks designers to build a JavaScript UI for the Ruby backend.}
        \item {Built an automated hotel check-in system for corporations with frequently traveling employees.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
